---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# keywords

<!-- badges: start -->
<!-- badges: end -->

You can use {keywords} to generate keywords for systematic reviews from PDF documents. Additionally a function is included to produce PRISMA diagrams

## Installation

{keywords} isn't yet on CRAN but you can get it from [GitHub](https://github.com/conig/keywords) using:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("conig/keywords")
```
## Generating keywords

To generate keywords, you just need to provide {keywords} with the path to a PDF or a folder of PDFs. Text must be extractable from those PDFs.

An example paper is included in this package which we will use to generate some keywords.

```{r example}
library(keywords)
path_to_pdf = system.file("example.pdf", package = "keywords")
```

Now we simply provide the number of topics, and keywords we want produced. {keywords} performs topic modelling on the input PDF(s) to return the top words related to each topic.

```{r}
set.seed(1) # to make the results reproducible

keywords(path_to_pdf,
         n = 5,
         topics = 1)
```

The example paper was a meta-analysis of Indigenous Australian drinking patterns.

## PRISMA diagram

To create a PRISMA diagram, you simply need to provide the number of records at each stage of your systematic review, and provide reasons for exclusions. Here's an example:

```{r out.width = "60%"}
prisma(
  database_records = 1250,
  additional_records = 35,
  after_duplicates_removed = 1134,
  fulltext_screened = 60,
  reasons = list(
    "No original data" = 20,
    "TL;DR" = 10,
    "Weird font" = 5,
    "Misc" = 6
  ),
  final = 19
)
```

